|

### 2021-05-21 appendix/appendix.Rmd
fixes typos and updates pdf

The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita is available below.

@@

We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita. Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

@@

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the expenduture per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

@@

Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers negative displaying negative effects. The random effects model for the subgroup is 0.22, which is negative but non-significant. Improve the estimation technique, for the case of IVs, render still a null effect of legislature size on per capita government expenditure.

@@

The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.

>>>>

The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita are available below.

@@

We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita. Both coefficients are not statistically significant, and they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

@@

Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenduture per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

@@

Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers displaying negative effects. The random effects model for the subgroup is 0.22, which is negative but non-significant. Improving the estimation technique, for the case of IVs, still renders a null effect of legislature size on per capita government expenditure.

@@

The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems. In the theoretical section below, we explain why the argument has potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.
